Treating Similarity with Respect: How to Evaluate Models of Meaning?

### 2016-06-13 paper.tex
Updates from ShareLaTeX

Since there is no way of deciding upfront whether there is a similarity relation between two words, the data collection procedure needs to test for both: relation existence and its strength. Numerical values, as has been shown in the introduction, do not fit this role, because of ambiguity. One way of avoiding the issue is to avoid asking humans for numerical similarity judgements, but instead to ask them to list commonalities and differences between the objects. As one might expect, similarity scores correlate with the number of listed commonalities \cite{markman1991commonalities,Markman1996,medin1993respects}. For incomparable pairs, the commonality list should be empty, but the differences will enumerate properties that belong to one entity, but not another \cite{markman1991commonalities,medin1993respects}.

>>>>

Since there is no way of deciding upfront whether there is a similarity relation between two words, the data collection procedure needs to test for both: relation existence and its strength. Numerical values, as has been shown in the introduction, do not fit this role, because of ambiguity. One way of avoiding the issue is to avoid asking humans for numerical similarity judgements, but instead to ask them to list commonalities and differences between the objects. As one might expect, similarity scores correlate with the number of listed commonalities \cite{markman1991commonalities,Markman1996,medin1993respects}. For incomparable pairs, the commonality list should be empty, but the differences will enumerate properties that belong to one entity, but not another \cite{markman1991commonalities,medin1993respects}. Verbally produced features (norms) for empirically derived conceptual representation of \newcite{McRae2005} is a good example of what data should be collected. But in contrast to \newcite{McRae2005}---where explicit comparison of concepts was avoided---participants should be asked to produce commonalities as part of similarity comparison.
